Characterizing Stellar Streams by ML

### 2023-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{Caption: .}
            TODO:
            \begin{enumerate}
                \item Get rid of the dropout in the plot
                \item the linear density in the stream-fraction plot
            \end{enumerate}
            \label{fig:mock_data_result}
        \end{figure*}

@@

@@

            Since this prior is equi-probable in the region $\mu - w < x < \mu + w$, the  impact is to encourage the stream to fall anywhere within this region. 
            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$.
            \begin{small}
            \begin{equation}
                \ln \pdf(x,\mu,w) \propto \tau \begin{cases} 
                    -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
                    0 & \mu - w \leq x < \mu + w \\
                    -\left(x-(\mu+w)\right)^2 & \mu + w \leq x
                \end{cases},
            \end{equation}\end{small}
            where the additive normalization is 
            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$

@@

        The result of applying our density model to the synthetic data is illustrated in \autoref{fig:mock_data_result}. The top panel shows the weight parameter that controls membership probability as a function of $\phi_1$. The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth. \JN{todo: maybe the kde should be a histogram}, the second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane. Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream. The are additional variations  mostly around the edges of the stream, though re-sampling the neural network weights with dropout reveals that these variations represent regions of higher model uncertainty.

>>>>

            % link to the code!
            In the code we offer a few ansatz for the PDMF. The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$. Any user-defined function may be used

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{Caption: .}
            TODO:
            \begin{enumerate}
                \item the linear density in the stream-fraction plot
            \end{enumerate}
            \label{fig:mock_data_result}
        \end{figure*}

@@

            \todo[inline]{}

@@

            Since this prior is equi-probable in the region $\mu - w < x < \mu + w$, the  impact is to encourage the stream to fall anywhere within this region. 
            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$.
            \begin{small}
            \begin{equation}
                \ln \pdf(x,\mu,w) \propto \tau \begin{cases} 
                    -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
                    0 & \mu - w \leq x < \mu + w \\
                    -\left(x-(\mu+w)\right)^2 & \mu + w \leq x
                \end{cases},
            \end{equation}\end{small}
            where the additive normalization is 
            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$. In this form we see that $\tau$ may be increased to strengthen the prior and encourage $\mbs{\theta}$ to pass through

@@

        The result of applying our density model to the synthetic data is illustrated in \autoref{fig:mock_data_result}. The top panel shows the weight parameter that controls membership probability as a function of $\phi_1$. The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth. The second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane. Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream. The are additional variations  mostly around the edges of the stream, though re-sampling the neural network weights with dropout reveals that these variations represent regions of higher model uncertainty.
